
% Packages
\documentclass[a4paper,10.9pt]{article}
\usepackage[left=3em,right=3em,top=2em,bottom=4em]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{changepage}
\usepackage{multicol} % Add this to your preamble
\usepackage{fontawesome} % For web icons
\usepackage{tcolorbox}
\linespread{0.995} % Adjusts line spacing to be tighter

%\usepackage{fontspec}
%\setmainfont{Calibri} % Replace "Font Name" with your desired font, e.g., Times New Roman

\setlength{\parindent}{0pt}
% Define custom colors
\definecolor{hyperlinks}{HTML}{000000}%{6d9eeb}
\definecolor{grey}{HTML}{555555}

% Setup hyperlink colors
\hypersetup{
    colorlinks = true,
    urlcolor=hyperlinks, % This sets the color of hyperlinks
}

% Custom commands
\newcommand{\resumetitle}[1]{{\LARGE\bfseries #1}\vspace{10pt}}
\newcommand{\sectiontitle}[1]{
  \begin{tcolorbox}[colback=black, colupper=white, sharp corners, boxrule=0pt, boxsep=3pt, left=0pt, right=0pt, top=1pt, bottom=1pt]
    \Large\bfseries #1
  \end{tcolorbox}
}
\newcommand{\majorposition}[1]{{\hspace{0pt}\Large\bfseries #1}\vspace{0.2em}}
\newcommand{\position}[1]{\Large\bfseries #1}\vspace{0.2em}
\newcommand{\bulletitem}[1]{\item #1\vspace{0.1em}}
\newcommand{\normaltext}[1]{#1}
\newcommand{\graytext}[1]{\textcolor{grey}{#1}} % Corrected usage of \textcolor
\newcommand{\white}[1]{\textcolor{white}{#1}}
\newcommand{\link}[2]{\href{#1}{\textcolor{hyperlinks}{#2}}} % Corrected for hyperlink color
\newtcolorbox{mybox}[1][]{
    colback=gray!10, % Lighter gray background
    colframe=black, % Black frame
    colupper=black, % Black text for readability
    sharp corners,
    boxrule=0.5pt,
    left=1pt,
    right=1pt,
    top=1pt,
    bottom=1pt,
    #1
}
\newcommand{\boxedtext}[1]{\begin{mybox}#1\end{mybox}}

% Set itemize spacing
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}
\thispagestyle{empty}
% Header
\begin{center}
\noindent{\Huge\textbf{Sahand Sorouri}}\\
\vspace{7pt}
{\textbf{\LARGE{Product Manager}}}\\
%\href{https://example.com}{Visit our website \faExternalLink{}}
\normalsize
\graytext{Iran, Open to relocate} $\cdot$ \href{mailto:sahand.sorouri@gmail.com}{sahand.sorouri@gmail.com} $\cdot$ \graytext{+1 (415) 800 4011}
\\
\href{https://linkedin.com/in/sahand-sorouri}{linkedin.com/in/sahand-sorouri \faExternalLink{}} $\cdot$ \href{https://sahand.sorouri.com}{sahand.sorouri.com \faExternalLink{}}
\end{center}
{Dynamic Product Manager with 5+ years of expertise in launching and scaling eCommerce platforms, skilled at optimizing the customer journey from booking to post-service engagement. Led the full product lifecycle, excelling in user experience enhancement and strategic development for both B2B and B2C sectors. Demonstrated success in amplifying user engagement and driving revenue growth by implementing innovative product solutions tailored to diverse customer needs and market demands.}
%\vspace{5pt}
{\boxedtext{\textbf{Core Competencies: }Experimentation \& A/B Testing, Data-driven Decision Making, Market Research, Cross-functional Collaboration, Product Strategy, Product Roadmap, Growth Strategy\\
\textbf{Technical Proficiencies:} Agile Scrum, Agile Kanban, Lean Startup, Notion, Miro, Jira, Figma, SQL, Google Analytics, Power BI, Mixpanel, Python, Latex, Prompt Engineering}}
%\vspace{3pt}
% Work Experience
\sectiontitle{Work Experience}
{\majorposition{\href{https://snappfood.ir}{SnappFood Company \faExternalLink{}}} \hfill\Large{\textbf{\graytext{2018 - 2023 [5 years]}}}}\\
{\small{\graytext{eCommerce Marketplace, Food Tech, B2B, B2C, Web \& Mobile}}\\
\small\graytext{Leading food delivery platform: +10 million monthly transactions, 4 million MAU, 80,000 partners, and 2,000 employees.}}
\vspace{5pt}
\begin{adjustwidth}{0.5cm}{0cm}

{{\position{Head of Product, }\large{\href{https://qbar.ir/container}{QBAR Startup \faExternalLink{} }}}{\small{\graytext{(SnappFood Company’s Initiative)}}}\hfill \large\graytext{Mar 2022 – Aug 2023}}
\\
{\small\graytext{QBAR a QR-facilitator, with more than million monthly unique visitors and +3,000 active B2B subscription}}
\begin{adjustwidth}{0.5cm}{0cm}
\normalsize
\begin{itemize}
  \bulletitem{Led recruitment and management of a diverse 20-member team across product, design, marketing, operations, and engineering, establishing an efficient and collaborative team structure.}
  \bulletitem{Accelerated partner onboarding process, decreasing the timeline from 30 days to 3 days(-90\%),utilizing data-driven approaches, automating CRM processes, and enhancing operational efficiency.}
  \bulletitem{Developed product roadmap, KPIs, and business plan, securing funding for expansion across the country while maintaining expenses at the same level.}
  \bulletitem{Improved user experience metrics up to 50\% by implementing user-centered design principles, including A/B testing, user research, and feedback loops with more than 100 partners.}
\end{itemize}
\end{adjustwidth}
\vspace{3pt}

{{\position{Senior Product Manager}}\hfill {\large\graytext{Mar 2021 – Feb 2022}}}
\\
{\small\graytext{Focusing on key strategic projects, working directly with SnappFood Chairman of the board}}
\normalsize
\begin{adjustwidth}{0.5cm}{0cm}
\begin{itemize}
  \bulletitem{Executed the multi-stakeholders, cross-company Iraqi food delivery platform, achieving a successful and well-functioning localized platform launch with 10,000 orders per month.}
  \bulletitem{Established a delivery service model as an extension of the vendor management system, integrating PoS, resulting in a fleet of 50 dedicated bikers, ensuring thousands of orders fulfilled per month.}
  \bulletitem{Launched SnappFood’s Cash-On-Delivery SaaS product, simplifying debit card payments, increasing transaction ratio by 5\%, and enhancing customer experience quality by 50\% for target customers.}
\end{itemize}
\end{adjustwidth}
\vspace{3pt}

{{\position{Product Manager}}\hfill \large\graytext{Mar 2020 – Feb 2021}}
\normalsize
\begin{adjustwidth}{0.5cm}{0cm}
\begin{itemize}
  \bulletitem{Led integration of SnappShop QCommerce platform into SnappFood, achieving a successful launch with 200,000 monthly orders in 2022.}
  \bulletitem{Launched SnappShop logistics management product, Shopex, resulting in the establishment of new hubs for dispatching SnappShop orders, reducing operational costs by 15\%.}
  \bulletitem{Improved SnappShop’s content management, optimizing seller onboarding and creating 60,000+ unified products using data science. Reduced seller onboarding time from 30 days to one week.}
\end{itemize}
\end{adjustwidth}
\vspace{3pt}

{{\position{Associate Product Manager}}\hfill \large\graytext{Sep 2018 – Feb 2020}}
\normalsize
\begin{adjustwidth}{0.5cm}{0cm}
\begin{itemize}
  \bulletitem{Initiated a Growth Product Strategy team of 5 people, creating infrastructure and monitoring business service KPIs, OKRs, and targets, resulting in achieving targets 60\% closer within the first year.}
  \bulletitem{Expanded SnappFood’s online supermarkets from 200 in Tehran to double that number in 10 cities within just one month during the pandemic, leading to a 20\% increase in daily orders.}
  \bulletitem{Designed a new delivery price segmentation feature, reducing delivery costs by up to 20\% annually.}
  \bulletitem{Introduced an advertising in-app product launch plan, allowing vendors to bid on service-areas to promote offerings on the SnappFood customer app.}
\end{itemize}
\end{adjustwidth}
\end{adjustwidth}

% Adjusting Education, Interests, and Case Studies into a three-column layout

\vspace{7pt}
\begin{center}
\noindent\begin{minipage}{0.32\textwidth}
  \sectiontitle{Education}
  Sharif University of Technology\\
  Bachelor of Electrical Engineering with
  \\
  a Minor in CS \hfill (2013 - 2018)
  \\
  \graytext{{Ranked 9th} in the National University Entrance Exam among 300k students} 
\end{minipage}%
  \hfill
  \begin{minipage}{0.32\textwidth}
  \sectiontitle{Interests}
  Artificial Intelligence
  \\
  Chess and Strategic Games
  \\
  Bouldering (Rock Climbing)
  \\
  Travel and Exploration
  \\
  Volunteer/Community Services
  \end{minipage}%
  \hfill
\begin{minipage}{0.32\textwidth}
  \sectiontitle{Certificates}
  \href{https://www.credly.com/badges/d370d9c3-e34d-46f4-a4bf-ef5c8fc42cd1/linked_in_profile}{AI for Product Management Cert. \faExternalLink{}}\\
  \href{https://www.linkedin.com/learning/certificates/870c0fd2f066e7b8503e479c2490fafd5882f912ff675c28901dc0718ee39ed9}{Aha! Product Management Cert. \faExternalLink{}}\\
  Active \href{https://adplist.org/certifications/144451}{ADPList Mentee \faExternalLink{}} \\
  Data Analysis \href{https://www.linkedin.com/learning/certificates/ffca4d550b1e4b91b668313ff2bf815beb1a5e1ab6fd508e4ed9188aafe2db28?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base_certifications_details%3BfdmfS%2FgnTKqHBLUxxTyUPQ%3D%3D}{\faExternalLink{}}, \href{https://www.linkedin.com/learning/certificates/cb5129fee28b086cddf3d21cbfeed021530abfbebfa7fa4a8f8964d9b7aa3c32?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base_certifications_details%3BfdmfS%2FgnTKqHBLUxxTyUPQ%3D%3D}{\faExternalLink{}}\\
  Statistics \href{https://https://www.linkedin.com/learning/certificates/b30b4d5c833c3a100d3be45f7897425ec2152b81b473b240359e358ce2c128d8}{\faExternalLink{}}, \href{https://www.linkedin.com/learning/certificates/1d347521f9fc7171d89c71a1b1944ce84c5e74870d3e73956425be407dd61258}{\faExternalLink{}}, \href{https://www.linkedin.com/learning/certificates/6422926178665f0c37e9fd93754684319febdbfa2a3b75db1f243990005333f6}{\faExternalLink{}}\end{minipage}

%  \sectiontitle{Case Studies}
%  Startup Budget Constraints \\
%  Overcoming Sales Targets \\
%  Adaptability Lessons Learned \\
%  Automating Vendor Onboarding \\
%  International Successful Launch
\end{center}
\end{document}

